Supplemental Information: remote sensing riverine gas exchange and estimating carbon efflux using SWOT observations

### 2021-02-18 supp_v1.Rmd
manuscript edits

---
title: "Supplemental Information: remote sensing riverine gas exchange and carbon efflux using SWOT observations"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: rse_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

@@

##Text S2
In Figure S4 we show that bed roughness only exerts an influence on $k_{600}$ when rivers are incredibly steep. We do this using the 'Keulegan effective roughness height' for the channel bed, which is detailed in equation S1 below (in the form form [@dingmanAnalyticalDerivationAtastation2007b]). This model was first outlined in the 1930s by Keulegan and outlined explicitly in [@fergusonHydraulicsHydraulicGeometry1986a] and [@dingmanAnalyticalDerivationAtastation2007b] in the context of hydraulic geometry (noting that it is a more generalized form of the Manning's and Chezy's velocity~depth relations commonly used in the literature). The model arises from depth integrating the Prandl-von Karman equation for velocity in a turbulent boundary layer ($\frac{u}{u_\star}=2.5ln(\frac{30y}{k_s})$) [@fergusonHydraulicsHydraulicGeometry1986a].

@@

Table S1 Details on the 3 velocity rating curve models used to estimate bulk carbon efflux from the SWOT rivers (section 5.2.4).
	Equation	Description
Raymond et al. (2012)	lnV=-1.64+0.285lnQ	Trained on Raymond et al. (2012) dataset
Raymond et al. (2013)	lnV=mean{█(-1.64+0.285lnQ,@-1.06+0.12lnQ  )}	Average of Raymond et al. (2012) model and one trained on 9,811 USGS streamgauges
Lauerwald et al. (2015)	lnV=-1.06+0.12lnQ	Borrowed from ½ of the Raymond et al. (2013) calculation (trained on 9,811 USGS streamgauges)

>>>>

---
title: "Supplemental Information: remote sensing riverine gas exchange and estimating carbon efflux using SWOT observations"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: rse_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

@@

##Text S2
In Figure S4 we show that bed roughness only exerts an influence on $k_{600}$ when rivers are incredibly steep. We do this using the 'Keulegan effective roughness height' for the channel bed, which is detailed in equation S1 below [in the form from @dingmanAnalyticalDerivationAtastation2007b]. This model was first outlined in the 1930s by Keulegan and outlined explicitly in [@fergusonHydraulicsHydraulicGeometry1986a] and [@dingmanAnalyticalDerivationAtastation2007b] in the context of hydraulic geometry (noting that it is a more generalized form of the Manning's and Chezy's velocity~depth relations commonly used in the literature). The model arises from depth integrating the Prandl-von Karman equation for velocity in a turbulent boundary layer [@fergusonHydraulicsHydraulicGeometry1986a].

@@

*Table S1: Details on the 3 velocity rating curve models used to estimate bulk carbon efflux from the SWOT rivers (section 5.2.4).*

|**Name**|**Equation**|**Description**|**Reference**|
|-------------|-------------|-------------|-------------|-------------|
|Raymond 2012|$ln(V)=-1.64+0.285ln(Q)$|Trained on their dataset|@raymondScalingGasTransfer2012a|
|Raymond 2013|$ln(V)=mean(-1.64+0.285ln(Q),  -1.06+0.12ln(Q))$ |Average of the Raymond 2012 equation and one trained on 9,811 USGS streamgauges|@raymondGlobalCarbonDioxide2013a|
|Lauerwald 2015|$ln(V)=-1.06+0.12ln(Q)$ |Borrowed from ½ of the Raymond 2013 calculation (trained on 9,811 USGS streamgauges)|@lauerwaldSpatialPatternsCO22015|
